---
title: “Lab 6“
author: Rachel Delorie
format: html
execute:
  echo: true
---
```{r}
# setup
library(tidymodels)
library(recipes)
library(yardstick)
library(ggthemes)
library(ggplot2)
library(parsnip)
library(tidyverse)
library(powerjoin)
library(purrr)
library(glue)
library(vip)
library(baguette)

root  <- 'https://gdex.ucar.edu/dataset/camels/file'
download.file('https://gdex.ucar.edu/dataset/camels/file/camels_attributes_v2.0.pdf', 
              'data/camels_attributes_v2.0.pdf')
types <- c("clim", "geol", "soil", "topo", "vege", "hydro")
# Where the files live online ...
remote_files  <- glue('{root}/camels_{types}.txt')
# where we want to download the data ...
local_files   <- glue('data/camels_{types}.txt')
walk2(remote_files, local_files, download.file, quiet = TRUE)
# Read and merge data
camels <- map(local_files, read_delim, show_col_types = FALSE) 
camels <- power_full_join(camels ,by = 'gauge_id')
```


```{r}
map_aridity <- ggplot(data = camels, aes(x = gauge_lon, y = gauge_lat)) +
  borders("state", colour = "gray50") +
    labs(color = "Aridity", title = "Aridity") +
   geom_point(aes(color = aridity)) +
  scale_color_gradient(low = "blue", high = "red") +
  ggthemes::theme_map()

map_pmean <- ggplot(data = camels, aes(x = gauge_lon, y = gauge_lat)) +
  borders("state", colour = "gray50") +
   geom_point(aes(color = q_mean)) +
  scale_color_gradient(low = "lightblue", high = "darkblue") +
  labs(color = "p_mean", title = "Mean Daily Precipitation") +
  ggthemes::theme_map() 
  
combined_maps <- map_aridity + map_pmean + plot_layout(ncol = 1)

